The Astropy Project

### 2017-11-21 main.tex
edits from tom

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of the \astropypkg.  Development of the \astropypkg is supported
through contributions by individuals to work on astropy in their own personal
time, contributions from individuals or groups to work on \astropy as 
part of a research project, or contributions from institutes that allocate 
people to work on \astropy. 
A list of organizations that have contributed to \astropy
are listed in the Acknowledgements.  
Different models have been proposed for the support of astropy 
(ie. \cite{2016arXiv161003159M}), 
but a sustainable, community-based model has not yet been established.
The astropy project has the ability to accept financial contributions 
(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS 
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative, 
open source scientific computing.},  
which generally covers the direct costs incurred by the \astropy project
along with supporting

>>>>

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of the \astropypkg.  Development of the \astropypkg is supported
by individuals who work on \astropy project in their own personal
time, by individuals or groups to work on \astropy as 
part of a research project, or contributions from institutes that allocate 
people to work on \astropy. 
A list of organizations that have contributed to \astropy
are listed in the Acknowledgements.  
Different models have been proposed for support of \astropy in the future 
(ie. \cite{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions 
(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS 
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative, 
open source scientific computing.},  
which generally covers the direct costs incurred by the \astropy project.
